Hi! 

This template is a combination of multiple student and teacher PFE report templates that I have compiled into one that hopefully will satisfy your needs.

It is in English, but I have included the french "Page de garde" if you want to use it, and the rest of the paper is easily translatable.

This document is compiled using pdfLatex Compiler, so make sure you select it in the menu on the top left of the page. You can change the font size there along with other things.

Some table, figure, list or formatting codes can be found in the "Codes\_needed.tex" file in this same folder, use them well.

The organisation of this template is as follows: 

The main compilation file is main.tex, any file you want to add, should be added there using, \input{Chapters/Chapter1} for example. Remember to change the PDF Title and author name before the begin document command.

Packages.tex is where you import packages and could modify their options.

The frontmatter folder contains unnumbered chapters that come before the actual chapters, so the resumes and acknowledgments are there. The pages are numbered in Roman numbers.

The chapters folder obviously contains the main chapters of the report, usually the first one is an intro, of both the project and the company, the last one is a conclusion chapter, I made it unnumbered here but you do you.

The endmatter folder contains the appendices, acronyms, glossary, and Complementary figures, tables and codes. Consider checking this link \url{https://libguides.usc.edu/writingguide/appendices} for more info. Usually you add an appendix for each subject you'll talk about it, each with its own codes, tables, figures and text.

The bibliography can be found at the end of main.tex file.

And to organise your figures better, upload the logos to the logos folder, and content related figures should go in the figures folder, where you can add sub folders.

Along the template, make sure to read my comments, they can be helpful to understand the purpose of a command or option. 

When you finish writing your thesis, make sure to verify that you didn't leave any generic line or link. Revise it well.

There are 10 warnings that show up in this template, some I couldn't manage to solve (or understand), and some I left since they are necessary for what I intend of this template.

Obviously this template is only a suggestion, it is not perfect in any sense, you can improve it in the way that suits you, so search away, and get used to reading the documentation.

Also consult with your supervisor, as each teacher has their own opinion on what constitutes the ideal report.

Finally, I hope you have enjoyed your time at INPT as much as I did, and Good Luck :D

-Mery